---
title: "Palm Trees Data Exploration"
subtitle: "Tidy Tuesday 2025-03-18" 
author: "Sarah Thomson"
date: 2025-04-27
format: html
editor: source
---

```{r message=FALSE}
library(tidyverse)
```


```{r data, message=FALSE}
palmtrees <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/main/data/2025/2025-03-18/palmtrees.csv')
```

Research question: Is there a relationship between the number of leaves a palm has and the size of its fruit? Maybe a palm with more leaves can produce bigger fruit. Does this relationship change for different subfamilies?

```{r}
palmtrees %>%
  ggplot(aes(y=max_fruit_width_cm, x=max_leaf_number))+
  geom_point()+
  geom_smooth(method="lm", se=FALSE)+
  facet_wrap(~palm_subfamily)+
  theme_classic()+
  labs(x="maximum number of leaves", y="maximum fruit width (cm)", title="Number of leaves vs size of fruit in different palm subfamilies")
```

Interpretation: The relationship between number of leaves and size of fruit varies depending on subfamily. In Arecoideae and Coryphoideae, there seems to be a positive correlation. This is less clear in the other subfamilies, with a possible negative correlation in Calamoideae. 